Robots, Are They Overlords or Serf-Laborers?

### 2015-06-10 draft1.tex
Final Commit for 6/9/15

@@

By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this slave-like definition has altered to something brand new as technology advances. In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics. These two definitions emphasize different aspect of Robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition. Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.

@@

Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.

@@

\section{Conclusion}
\subsection{v1}
As the research studies toward the creation of AI deepens, this technological advancements will raise more ethical problems. Regardless of the sources of issues, these problems relate to AI's definition and its responsibilities. It is crucially important to decide whether or not robots are simply functional machine that is utilitarian in its responsibilities and nothing more. If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code. However, the results of recent studies indicate that in near future individuals may possess personal robots interacting closely with their master. In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention. If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots, which are closely related to the terms of AI, will also evolve rapidly to its excellence. The only limitation in its experimental progress should be the initial motivations which must permanently coded to create anti-behaviors constraining its action-decision chain.
\subsection{v2}
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients. However, these two prominent terms of technology closely resembles another, the Internet. As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved. 
\bibliographystyle{apacite}
\bibliography{bibliography}
\end{document}

>>>>

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)

@@

By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances. In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics. These two definitions emphasize different aspect of robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition. Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.

@@

Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within robotics exemplifies another complex issue.

@@

\section{Conclusion}
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
%However, these two prominent terms of technology closely resembles another, the Internet.
%, otherwise yet another issue will jump into debate topics before formers could be solved. 
Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more. If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI. In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention. If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence. As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved. 
\bibliographystyle{apacite}
\bibliography{bibliography}
\end{document}
